---
title: "p8105_hw1_ml4198"
output: html_document
---

```{r setup}
library(tidyverse)
```

## Problem 1

```{r df_create}
problem1_df = tibble(
  x = rnorm(10),
  vec_logical = c(TRUE, TRUE, TRUE, FALSE, FALSE, TRUE, TRUE, TRUE, FALSE, FALSE),
  vec_char = c("this", "is", "a", "character", "vector", "of", "length", "at", "least", "ten"),
  vec_factor = factor(c("red", "red", "blue", "blue", "yellow", "red", "red", "blue", "blue", "yellow"))
)

problem1_df

mean(problem1_df$x)
mean(problem1_df$vec_logical)
mean(problem1_df$vec_char)
mean(problem1_df$vec_factor)
```

Mean of x and vec_logical can be taken, however mean of character and factor vectors is not available.

```{r as.numeric}
as.numeric (problem1_df$vec_logical)
as.numeric (problem1_df$vec_char)
as.numeric (problem1_df$vec_factor)
```

The logical and factor functions can be converted to numeric values, however character function cannot.

```{r convert}
as.numeric (problem1_df$vec_logical) * (problem1_df$x)
as.factor (problem1_df$vec_logical) * (problem1_df$x)
as.numeric (as.factor (problem1_df$vec_logical)) * (problem1_df$x)
```

## Problem 2

```{r penguins}
data("penguins", package = "palmerpenguins")

nrow(penguins)
ncol(penguins)
mean (penguins$flipper_length_mm, na.rm=TRUE)
```

This is a dataset of 8 variables (species, island, bill length, bill dpeth, flipper length, body mass, sex, year) with 344 observations. The mean flipper length is 200.9152 mm.

```{r scatter}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```
